Exploring Determinants of Child Mortality Globally (2022): The Role of Vaccination, Healthcare Spending, and Nutrition

### 2025-04-15 paper/paper.qmd
Result

>>>>

```{r}
#| label: fig-mor1
#| fig-cap: "Performance of two new proposed loss functions compared to crossentropy loss. They are evaluated based on number of correct labels in the top 100 labels predicted by the neuronetwork, roughly 10% of all the testing data. We see that rank loss does not outperform crossentropy loss while focal loss did but there is no promising beatens since the error bars contain each other's mean." 
#| echo: false
#| warning: false
#| message: false
# Load required libraries
library(ggplot2)
library(dplyr)

# Define data
mlp <- c(36, 34, 38, 40, 44, 39, 42, 37, 40, 42)
ranknet <- c(34, 35, 33, 40, 44, 40, 44, 39, 42, 37)
focal <- c(35, 38, 39, 41, 41, 40, 50, 40, 43, 41)

# Create a data frame
df <- data.frame(
  Model = rep(c("MLP", "RankNet", "Focal Loss"), each = 10),
  Correct = c(mlp, ranknet, focal)
)

# Summarize: compute means and standard deviations
summary_df <- df %>%
  group_by(Model) %>%
  summarise(
    Mean = mean(Correct),
    SD = sd(Correct)
  )

# Plot
ggplot(summary_df, aes(x = Model, y = Mean, fill = Model)) +
  geom_bar(stat = "identity", width = 0.6, color = "black") +
  geom_errorbar(aes(ymin = Mean - SD, ymax = Mean + SD), width = 0.2) +
  geom_text(aes(label = round(Mean, 1)), vjust = -0.5, size = 5) +
  labs(
    title = "Performance of MLP, RankNet, and Focal Loss Models Across 10 Splits",
    y = "Correct Predictions in Top 100",
    x = ""
  ) +
  theme_minimal() +
  theme(
    legend.position = "none",
    text = element_text(size = 14)
  )

```
